\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[default]{sourcesanspro} % Tech-oriented font

% --- Geometry & Setup ---
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for maximum compactness
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% --- Custom Colors ---
\definecolor{techBlue}{RGB}{0, 90, 180} % A sharper, tech-focused blue

% --- Section Formatting ---
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries\color{black}
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% --- Custom Commands ---
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{\tiny\color{techBlue}$\bullet$}
\renewcommand\labelitemii{\tiny\color{techBlue}$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% --- RESUME STARTS ---
\begin{document}

% --- HEADING ---
\begin{center}
    {\Huge \textbf{INDIGO NOLAN}} \\ \vspace{4pt}
    \small 
    \faPhone\ 07775 156078 \ $|$ \ 
    \href{mailto:cv@indigonolan.com}{\faEnvelope\ \underline{cv@indigonolan.com}} \ $|$ \ 
    \href{https://indigonolan.com}{\faGlobe\ \underline{indigonolan.com}} \ $|$ \ 
    \href{https://github.com/Lem0naise}{\faGithub\ \underline{github.com/Lem0naise}} \ $|$ \ 
    \href{https://linkedin.com/in/indigonolan}{\faLinkedin\ \underline{linkedin.com/in/indigonolan}}
    \newline
    \faMapMarker* \ London / Southampton \ 
\end{center}


% --- EDUCATION ---
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southampton}{Southampton, UK}
      {MEng Computer Science $|$ Predicted First}{Expected 2028}
      \resumeItemListStart
        \resumeItem{\textbf{Academics:} A$^{*}$A$^{*}$A at A-Level, 11 A*s at GCSE.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


% --- SKILLS ---
% Moved up for immediate technical context
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, Java, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: Next.js, React, React Native, Node.js, GDScript} \\
     \textbf{DevOps \& Tools}{: Docker, Git, Vercel, Supabase, PostgreSQL, MongoDB, Linux/Bash, Google Cloud Platform (GCP)} \\
     \textbf{Spoken Languages}{: English (Native), French (B2), Russian (B2), German (B1)}
    }}
 \end{itemize}


% --- EXPERIENCE ---
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Southampton}{Jan 2026}
      {Research Assistant}{Southampton, UK}
      \resumeItemListStart
        \resumeItem{Collected data mapping  nighttime urban environments, integrating quantitative sensor data with qualitative metrics.}
        \resumeItem{Used hardware (luxmeters, GPS, spectrometers) to capture spatial light/color data, correlating it with user experience.}
      \resumeItemListEnd

    \resumeSubheading
      {Southampton University Students' Union}{June 2025 -- Present}
      {School President (Electronics \& Computer Science)}{Southampton, UK}
      \resumeItemListStart
        \resumeItem{Elected representative for 2,800 students; chaired the committee and liaised directly with senior faculty for curriculum improvements.}
        \resumeItem{Architected structural changes to the voting system, successfully fixing past under-representation issues.}
      \resumeItemListEnd

    \resumeSubheading
      {Shell AI}{July 2023}
      {Summer Intern}{London, UK}
      \resumeItemListStart
        \resumeItem{Analyzed machine learning models for optimizing real-time oil drilling operations to improve efficiency and safety.}
        \resumeItem{Co-designed and prototyped a social justice mobile application, pitching the UI/UX architecture to senior Experience Design leads.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


% --- PROJECTS ---
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{CashCat} $|$ \emph{Next.js, React, PostgreSQL, REST}}{\href{https://cashcat.app}{cashcat.app}}
      \resumeItemListStart
        \resumeItem{Full-stack financial application implementing zero-based budgeting principles with complex state management.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Climate Stories Library} $|$ \emph{Next.js, Supabase, Vercel, Google Cloud Platform \& APIs}}{\href{https://www.climatestorieslibrary.com}{climatestorieslibrary.com}}
      \resumeItemListStart
        \resumeItem{Designed a professional website and video backend for a climate organisation, increasing monthly engagement by 1300\% and connecting them with 40+ international clients.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{The Political Playground} $|$ \emph{React, Custom Simulation Engine}}{\href{https://pp.indigo.spot}{pp.indigo.spot}}
      \resumeItemListStart
        \resumeItem{Developed a complex election simulation engine featuring coalition mathematics and dynamic voter bloc logic.}
        \resumeItem{Designed an interactive UI similar to "The Campaign Trail" to gamify democratic education.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Fantasteroids} $|$ \emph{Godot, Steamworks API, GDScript}}{\href{https://store.steampowered.com/app/1790870/Fantasteroids/}{Fantasteroids on Steam}}
      \resumeItemListStart
        \resumeItem{Managed the full development lifecycle of a retro-arcade game, achieving a successful Steam marketplace launch with 300+ players and 90\% positive ratings.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{ESA AstroPi Challenge} $|$ \emph{Python, OpenCV, NumPy}}{}
      \resumeItemListStart
        \resumeItem{Wrote an image-processing algorithm deployed on the International Space Station to calculate cloud/land cover from orbit.}
        \resumeItem{Processed 200+ images daily with high efficiency in a constrained hardware environment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}